EGGs are adhesive!\\ An algebraic account of equality saturation

### 2025-08-23 jlamp/jlamp.tex
minima

\author[1]{Davide Castelnovo\corref{cor1}%
}
\ead{castelnovod@gmail.com}
%{https://orcid.org/0000-0002-5926-5615}{}

\author[1]{Fabio Gadducci}
\ead{fabio.gadducci@unipi.it}
%{https://orcid.org/0000-0003-0690-3051}{}

@@

@@

@@

>>>>

\author[1,mur]{Davide Castelnovo\corref{cor1}%
}
\ead{castelnovod@gmail.com}
%{https://orcid.org/0000-0002-5926-5615}{}

\author[1,mur]{Fabio Gadducci}
\ead{fabio.gadducci@unipi.it}
%{https://orcid.org/0000-0003-0690-3051}{}

@@

\fntext[mur]{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 
``Spatio-Temporal Enhancement of Neural nets for Deeply Hierarchical Automatised Logic'' (STENDHAL).}

@@

\begin{keyword}
Hypergraphs, terms graphs, e-graphs, adhesive categories.
\end{keyword}

@@

\section*{Acknowledgments}
Hypergraphs, terms graphs, e-graphs, adhesive categories.
